Empirical Study of Scientific Computer Software: Objectives and Research Questions

### 2020-06-12 OverallResearchProposal/ObjectivesAndResearchQuestions.tex

To fully explain this research objective, we will decompose each constituent
part in turn, starting with the end of the sentence.  In the above objective,
software consists of either programs, which run (execute) on a computer, or
libraries, which provide services to be used by programs.  Both programs and
libraries are created using computer code, written in a programming language.
Many developers place most, if not all, of their emphasis on the computer code
that makes up programs and libraries.  However, we consider the outcome of the
development process to be more than just software and the associated computer
code; we consider the products of the development process to be \{software +
artifacts\}.  The artifacts include code, but also all the other potential work
products, such as documentation, build scripts, test cases, contributor's
guides, etc.  From this point onward, we will use the term \emph{softifacts}
when we are referencing the combination of software and the associated
artifacts.  As we will explain below, assessing the quality of sustainability is not
possible by only considering the computer code; it depends on all of the
artifacts, and on the processes and methodologies used during software
development.  \wss{Can we consider software as both the computer code and the
  executable (program or library), or should the term software just mean the
  executable?  That is, when we mean code, should we be careful to not instead
  say software?}

We define sustainable softifacts, as follows: \emph{Sustainable softifacts
  satisfy, for a reasonable amount of effort, the software requirements for the
  present, while also being maintainable, reusable and reproducible for the
  future.}  This definition is a specialization of the general definition of
sustainable development from \citet{Brundtland1987}, as discussed in
Section~\ref{Sec_Context}.  The notion of ``reasonable effort'' is part of the
definition of sustainability, but reasonable cannot be completely defined
because what is reasonable is going to depend on the context.  Problems that are
large, complex and/or critical are going to have a greater ``budget'' of time
and energy.  When comparing different alternatives for processes and
methodologies, preference would be given to the alternative that costs less
effort, assuming that this alternative achieves the same (or a higher) level of
sustainability as its competition.  \wss{reasonable effort, without a large
  cost, means productivity} The assumptions listed in the next section
(Section~\ref{Sec_Context}) outline the typical space of problems where it makes
sense to aim for sustainable softifacts.

The overall objectives asks what is needed for sustainability.  This ``what''
can be decomposed further.  We consider the ``what'' to be the principles,
processes and methodologies used for software development.  We exclude tools
from this list because, although tools are needed to support processes and
methodologies, tools change rapidly.  Our goal is to be general.  If the right
principles, processes and methodologies are found, the tools will adapt to
match.  However, understanding the current state of the practice will involve
looking at tools, as shown in the later list of research questions
(Section~\ref{Sec_ResearchQuestions}).

@@

@@

- what is needed to produce softifacts sustainably motivates our ideal process
(sequence of choices).

>>>>

To fully explain this research objective, we will decompose each constituent
part in turn.  In the above objective, \emph{software} consists of either
programs, which run (execute) on a computer, or libraries, which provide
services to be used by programs.  Both programs and libraries are created using
computer code, written in a programming language.  Many developers place most,
if not all, of their emphasis on the computer code that makes up programs and
libraries.  However, we consider the outcome of the development process to be
more than just software and the associated computer code; we consider the
products of the development process to be \{software + artifacts\}.  The
\emph{artifacts} include code, but also all the other potential work products,
such as documentation, build scripts, test cases, contributor's guides, etc.
From this point onward, we will use the term \emph{softifacts} when we are
referencing the combination of software and the associated artifacts.  As we
will explain below, assessing the quality of sustainability is not possible by
only considering the computer code; it depends on all of the artifacts, and on
the processes and methodologies used during software development.  \wss{Can we
  consider software as both the computer code and the executable (program or
  library), or should the term software just mean the executable?  That is, when
  we mean code, should we be careful to not instead say software?}

We define sustainable softifacts, as follows: \emph{Sustainable softifacts
  satisfy, with a reasonable amount of effort, the software requirements for the
  present, while also being maintainable, reusable and reproducible for the
  future.}  This definition is a specialization of the general definition of
sustainable development from \citet{Brundtland1987}, as discussed in
Section~\ref{Sec_Context}.  The notion of ``reasonable effort'' is part of the
definition of sustainability, but reasonable cannot be completely defined
because what is reasonable is going to depend on the context.  Problems that are
large, complex and/or critical are going to have a greater ``budget'' of time
and energy.  When comparing different alternatives for processes and
methodologies, preference would be given to the alternative that costs less
effort, assuming that this alternative achieves the same (or a higher) level of
sustainability as its competition.  Achieving a reasonable effort means that
sustainability depends on the productivity the adopted development and
maintenance process.  The assumptions listed in the next section
(Section~\ref{Sec_Context}) outline the typical space of problems where it
sustainable softifacts are necessary, and what problem constraints suggest the
possibility of a reasonable level of effort.

The overall objectives asks what is needed for produce softifacts sustainably.
We consider the \emph{what} to be the principles, processes and methodologies
used for software development.  We exclude tools from this list because,
although tools are needed to support processes and methodologies, tools change
rapidly.  Our goal is to be general.  If the right principles, processes and
methodologies are found, the tools will adapt to match.  However, understanding
the current state of the practice will involve looking at tools, as shown in the
later list of research questions (Section~\ref{Sec_ResearchQuestions}).  As
mentioned above, for sustainability to be achieved, the productivity of the
adopted process must be considered.

@@

Traditional approach struggles.  Try generative.  Does generative supply what is
needed?  Is there an ideal process?  - what is needed to produce softifacts
sustainably motivates our ideal process (sequence of choices).

@@
